Algorithm Engineering

### 2022-11-19 Assignments/paper.tex
add 04_Code & Exam Assignments

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

>>>>

\subsection{Explain how divide and conquer algorithms can be parallelized with tasks in OpenMP.}
Divide and conquer algorithms recursively split down a problem until the pieces can be directly solved.
Such algorithms can be paralleized in OpenMP using the constructs taks and taskwait for the recursive call.
OpenMP tasks are independent work blocks. A queueing system dynamically handles the assignment of threads to the tasks. 
Each threads picks up a task from the queue and executes it. This goes on until the queue is empty. 
Tasks are defined within a parallel region and within a single construct, to make sure that one thread creates the tasks.
Taskwait is a construct that waits until all tasks are executed.

\subsection{Describe some ways to speed up merge sort.}
\begin{itemize}
	\item Tasks - With task and taskwait
	\item Avoid copying - to prevent that additional memory is created recursively and make sure that initially memory is instantiated and reused.
	\item if Clause - task will only be created, if a certain condition is true
	\item final Clause - tasks won't be created anymore, if a condition is true
\end{itemize}

\subsection{What is the idea behind multithreaded merging?}
The goal is to sort and merge two arrays using a divide and conquer algorithm. To do that we look at the median of the
array with more elements. Then we look at the other array and compare the elements smaller than the median and merge these
with the respective elements from the other array. That way merge is executed in parallel.

\subsection{Read What every systems programmer should know about concurrency. https://assets.bitbashing.io/papers/concurrency- primer.pdf
Discuss two things you find particularly interesting.}
The order of written code can be changed as compiler try to optimize it and rewrite code to run faster on the targeted hardware.
RAM hasn’t speeded up the way CPU processors have. This creates a widening gap between the instruction fetch and the time needed to retrieve data from memory.
To prevent reordering we can use atomic types in C or C++.

Atomicity means that something can’t be divided into smaller pieces. Threads need to use atomic reads and writes to share data. 
If they are not atomic they are so-called torn reads and writes.
To ensure atomicity one need to make sure that variables used for thread synchronization aren’t larger than the CPU word size.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
